{\plant}: A package for modelling forest trait ecology \& evolution

### 2015-11-09 ms.tex
Resolve final issues with figures
- changed location of two species in figure 5 and thus other figures two. Between our first and second submission to MEE the location
of the ESS moved slightly and we failed to notice. Have now updated.
- Figure patch needed more space on right, and formatting of numbers.

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=15cm,keepaspectratio]{figures/plant.pdf}
\caption{Physiological dynamics for individual plants varying in size,
 trait and light environment. Solid lines refer to the high-\textsc{lma} (leaf mass per unit leaf area) strategy (\textsc{lma} =
 0.267), while dashed lines refer to the low-\textsc{lma} strategy
 (\textsc{lma} = 0.08). (a) Growth trajectories are influenced by
 both light environment and traits. (b) Over time, the fraction of
 living tissue switches from leaf towards sapwood, with high-\textsc{lma} species having relatively more mass in leaf than low-\textsc{lma} species. (c)
 Size-dependent height growth rates, being the derivatives of the functions in (a), peak at a height of around
 5m, but the location of this peak varies with both trait and light
 level. (d) Declines in height growth rate with light level vary with plant size
 and traits. Whole-plant light compensation points (indicated by
 circles) emerge at zero growth rate (intercepts on horizontal axis).
 The light level used in (a) and (c) is indicated by
 coloured ticks. See Appendix \ref{sec:code} for code
 reproducing this figure.}
\label{fig:plant}
\end{figure}

>>>>

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=15cm,keepaspectratio]{figures/plant.pdf}
\caption{Physiological dynamics for individual plants varying in size,
 trait and light environment. Solid lines refer to the high-\textsc{lma} (leaf mass per unit leaf area) strategy (\textsc{lma} =
 0.2625), while dashed lines refer to the low-\textsc{lma} strategy
 (\textsc{lma} = 0.0825). (a) Growth trajectories are influenced by
 both light environment and traits. (b) Over time, the fraction of
 living tissue switches from leaf towards sapwood, with high-\textsc{lma} species having relatively more mass in leaf than low-\textsc{lma} species. (c)
 Size-dependent height growth rates, being the derivatives of the functions in (a), peak at a height of around
 5m, but the location of this peak varies with both trait and light
 level. (d) Declines in height growth rate with light level vary with plant size
 and traits. Whole-plant light compensation points (indicated by
 circles) emerge at zero growth rate (intercepts on horizontal axis).
 The light level used in (a) and (c) is indicated by
 coloured ticks. See Appendix \ref{sec:code} for code
 reproducing this figure.}
\label{fig:plant}
\end{figure}
